Investigating the Impact of Macroeconomic Indicators on the FTSE 250 Index and the Use of Machine Learning Methods to Forecast the Price of the FTSE 250 Index

### 2024-08-22 tex/paper.tex
data section revised

During the data collection process, it was necessary to address an issue raised by the fact that the Bank of England’s Monetary Policy Committee (MPC) 
does not convene on a monthly basis, and are not obligated to 
announce a rate on a regular basis. To address the resulting irregularities the data was adjusted using \algoref{interest_rate_adjustment}.

>>>>

For the interest rate data, it was necessary to address an issue raised by the fact that the Bank of England’s Monetary Policy Committee (MPC) 
does not convene on a monthly basis, and are not obligated to 
announce a rate on a regular basis. To address the resulting irregularities the data was adjusted using \algoref{interest_rate_adjustment}.
